Three 40 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-03-31 papers/ms.tex
update ms

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.41\textwidth]{f3a.pdf}
			\includegraphics[width=0.41\textwidth]{f3b.pdf}
		}

		\vspace{-1.45cm}	
		\subfloat{
			\includegraphics[width=0.41\textwidth]{f3c.pdf}
			\includegraphics[width=0.41\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Raw and processed light curves for the objects of
    interest.} Top: raw.  Bottom: processed.
    The increased scatter during transit is likely due to starspot
    crossing events.  KOI-7913 is janky, but P=24 days.
		\label{fig:planets}
	}
\end{figure*}

>>>>

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3a.pdf}
			\includegraphics[width=0.33\textwidth]{f3b.pdf}
		}

		\vspace{-1.27cm}	
		\subfloat{
			\includegraphics[width=0.33\textwidth]{f3c.pdf}
			\includegraphics[width=0.33\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.5cm}
	\caption{
		{\bf Raw and processed light curves for the Kepler Objects of
    Interest in Cep-Her.}   
    {\it Top}:
    50 day light curve segment from the 3.9 years of Kepler data.  The
    ordinate shows the \texttt{PDCSAP} median-subtracted flux in units
    of parts-per-thousand ($\times 10^{-3}$).  The dominant signal is
    induced by starspots.  
    {\it Bottom}:
    Phase-folded transits of Kepler-1643, KOI-7913, KOI-7368, and
    Kepler-1627 with stellar variability removed.  The maximum {\it a
    posteriori} transit model is shown with the gray line, and the
    residual after subtracting the transit model is vertially
    displaced.  Windows over 10 hours are shown.  Gray points are
    individual flux measurements; black points are binned to 20 minute
    intervals, and have a representative 1-$\sigma$ error bar in the
    center-right of each panel. 
		\label{fig:planets}
	}
\end{figure*}

\subsection{Kepler Data}

The Kepler space telescope observed Kepler-1643, KOI-7913, and
KOI-7368 at a 30-minute cadence between May 2009 and April 2013.  For
all three systems quarters 1 through 17 were observed without any data
gaps other than the usual quarterly roll.  The top panel of
Figure~\ref{fig:planets} shows a 50-day slice of the \texttt{PDCSAP}
light curves for the three new Cep-Her candidates, along with
Kepler-1627.  In \texttt{PDCSAP}, nonastrophysical variability is
removed through a cotrending approach that uses a set of basis vectors
derived using singular value decomposition of a set of
systematics-dominated stellar light curves
\citep{smith_kepler_PDC_2017}.  In our analysis, we used the
\texttt{PDCSAP} light curves with the default optimal aperture
\citep{smith_finding_2016}.  Cadences with non-zero quality flags were
omitted.  In all cases, the stars are dominated by spot-induced
modulation with peak-to-peak variability between 2\% and 10\%.  These
signals are much larger than the transits, which have depth
$\approx$0.1\%.
To quantify the stellar rotation periods, we calculated the
Lomb-Scargle periodogram for each Kepler quarter independently.  The
resulting means and standard deviations are quoted in
Table~\ref{tab:sysparams}.

\subsection{Transit and Stellar Variability Model}

Our goals in fitting the Kepler light curves are twofold.  First, we
want to derive accurate planetary sizes and orbital properties.
Second, we want to remove the stellar variability signal to enable a
statistical assessment of the probability that the transit signals are
planetary.

Our adopted approach was as follows.  Given an initial guess for the
transit ephemeris from the \texttt{q1\_q17\_dr25} analysis
\citep{thompson_planetary_2018}, the light curve was first trimmed to
a local window around each transit of duration $\pm 3\times t_{14}$.
The local out-of-transit points were then fitted with a fourth-order
polynomial, which was then divided out from the light curve.  The
resulting flattened transits were then fitted with a 
planetary transit under the assumption of quadratic limb darkening.
Our model therefore included 8 free parameters for the transit ($\{P,
t_0, \log R_{\rm p}/R_\star, b, u_1 ,u_2, R_\star, \log g\}$), 2 free
parameters for the light curve normalization and a white noise jitter
($\{\langle f \rangle, \sigma_f \}$), and an additional 5 implicit
parameters per transit through the polynomial.

We fitted the models using \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  We assumed a Gaussian likelihood, and
sampled using \texttt{PyMC3}'s No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}, after having initialized using the
maximum {\it a posteriori} (MAP) model.  We used the
\citet{gelman_inference_1992} statistic ($\hat{R}$) as our convergence
diagnostic.  Abbreviated results are in Table~\ref{fig:sysparams}, the
full results are in Appendix~\ref{app:transit}.

One weakness of our fitting approach is that we have fixed 5 implicit
parameters per individual transit to their MAP values to remove the
stellar variability signal.  An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using, say, a quasiperiodic Gaussian process (GP).  We
explored this approach, but found that it required careful fine-tuning
of the hyperparameter priors, otherwise the GP would tend to
incorporate anything that was not part of the transit, even if it was
short-term variability attributable to for instance flares, or simply
instrumental noise.  This failure mode is particularly pernicious, in
that it yields an inflated and ill-founded sense of confidence in the
transit model results.  While our model is simpler, it has the benefit
that its white noise jitter never trades off with any parameter
equivalent to a damping timescale for the coherence of the GP.  It is
also computationally efficient, while capturing the planetary
parameters that we actually care about.

\subsection{Planet Validation}

%TODO : write a paragraph or two about previous VESPA work, and how we
% went further.

% Previous analyses have identified and characterized the smaller
% transit signal \citep{2012ApJS..199...24T,thompson_planetary_2018},
% validated its planetary nature \citep{morton_false_2016}, and even
% searched the system for transit timing variations
% \citep{holczer_transit_2016}.  Nonetheless, since the cluster
% membership provides us with more precise stellar parameters than those
% previously available, we opted to reanalyze the light curve.
